Major Studio I \\ Final Project

### 2021-11-18 misc/biodesign.tex
small tweaks

\begin{document}
\maketitle
%\tableofcontents
%----------------------------------------------
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \tx
\textbf{Why you are interested in taking this class and participating in the Biodesign Challenge?}                                                                                                                                                                                                                                                                                                                                                                                                                                                   
I would like to take this course and participate in the biodesign challenge because I am trying to build a foundation of thought in the areas of biodesign and bioart. My prior background is in computer engineering and kinetic sculpture and I have always been fascinated by the field of biomimetics.

I am perpetually drawn to this field because of the ambiguity and contrast it highlights -- blurring the line between what we intuitively know to be natural and what we intuitively know to be man-made or artificial. Recently, I have been trying to pin down the importance and utility of this particular uncertainty in a broader research contex. The root of my curiosity in addressing the boundary between what is natural and artificial is a desire to understand how creative practitioners can use it to generate reflection and consideration of humanity's place in the natural world.

>>>>

\begin{document}
\maketitle
%\tableofcontents
%----------------------------------------------

\textbf{Why you are interested in taking this class and participating in the Biodesign Challenge?}

I would like to take this course and participate in the biodesign challenge because I am trying to build a foundation of thought in the areas of biodesign and bioart. My prior background is in computer engineering and kinetic sculpture and I have always been fascinated by the field of biomimetics.

I am perpetually drawn to this field because of the ambiguity and contrast it highlights -- blurring the line between what we intuitively know to be natural and what we intuitively know to be man-made or artificial. Recently, I have been trying to pin down the importance and utility of this particular uncertainty in a broader research contex. The root of my curiosity in addressing the boundary between what is natural and artificial is a desire to understand how creative practitioners can use the uncertainty surrouding thie distinction to generate reflection and consideration of humanity's place in the natural world.
